---
title: "p8105_hw6_bsr2136"
author: "Barik Rajpal"
date: "11/22/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(modelr)
```

## Problem 0

```{r p0, warning = F}
dir.create("files_for_hw6")
```

## Problem 1

### Loading the data, Cleaning it, and Checking for Missing Values

```{r p1 setup, message = F}
birthwt <- read_csv("./files_for_hw6/birthweight.csv")

birthwt <- birthwt %>%
  mutate(babysex = factor(babysex),
         frace = factor(frace),
         malform = factor(malform),
         mrace = factor(mrace),
         )

map(birthwt, ~sum(is.na(.)))
```

There are no missing values, and the 4 categorical variables are now factors.

### Proposed Regression Model

I'm using the step function, followed by checking the LM Adjusted R-Squared, and RSS to determine the optimal model. I'm hiding the results of this code chunk, as they take up a lot of space (especially the step function), but I will summarize them below.

```{r p1 regression model, results = F}
prop_reg_model1 <- step(lm(bwt ~., data = birthwt),direction = "backward")

summary(prop_reg_model1)

prop_reg_model2 <- lm(formula = bwt ~ babysex + bhead + blength + delwt + 
    gaweeks + mheight + mrace + parity + ppwt + smoken, data = birthwt)

summary(prop_reg_model2)

anova(prop_reg_model2,prop_reg_model1)

prop_reg_model3 <- lm(formula = bwt ~ babysex + bhead + blength + delwt + 
    gaweeks + mheight + mrace + ppwt + smoken, data = birthwt)

summary(prop_reg_model3)

anova(prop_reg_model3,prop_reg_model2)
```

I first built the model using the step function with direction = "backwards", which initially builds the model with all variables as predictors, then removes them one at a time and tests if the AIC decreases (which is indicative of better model fit). The model that the step function returned was:

lm(formula = bwt ~ babysex + bhead + blength + delwt + fincome + 
    gaweeks + mheight + mrace + parity + ppwt + smoken, data = birthwt)

I checked a summary of the model, and then removed the least significant variables and checked to see if the model's Adjusted R-Squared decreased significantly, and used an anova to test if the RSS was significantly decreased due to the additional variable. What I found was that removing "fincome" did not decrease the adjusted R-squared very much, and including "fincome" did not decrease the RSS very significantly, so I removed fincome from the model as well. I checked if removing "parity" would be similar, but the adjusted R-squared did decrease a bit, and an anova test suggested that including "parity" actually did decrease the RSS to a significant degree, so I left "parity" in the model, and my final model was:

lm(formula = bwt ~ babysex + bhead + blength + delwt + gaweeks + 
    mheight + mrace + parity + ppwt + smoken, data = birthwt)
    
### Plotting Residuals Against Fitted Values

```{r p1 plot}
birthwtdf <- add_residuals(birthwt, prop_reg_model2)
birthwtdf <- add_predictions(birthwtdf, prop_reg_model2)

birthwtdf %>%
  ggplot(aes(x=pred,y=resid)) + 
  geom_point(alpha=.5)
```

### Models to compare to

```{r}
model1 <- lm(bwt ~ blength + gaweeks, data = birthwt)

model2 <- lm(bwt ~ bhead * blength * babysex, data = birthwt)
```


## Problem 2

```{r pressure, echo=FALSE}
plot(pressure)
```


