---
title: "p8105_hw6_bsr2136"
author: "Barik Rajpal"
date: "11/22/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(modelr)
```

## Problem 0

```{r p0, warning = F}
dir.create("files_for_hw6")
```

## Problem 1

### Loading the data, Cleaning it, and Checking for Missing Values

```{r p1 setup, message = F}
birthwt <- read_csv("./files_for_hw6/birthweight.csv")

birthwt <- birthwt %>%
  mutate(babysex = recode(
                        as.factor(babysex),"1"="male","2"="female"),
         frace = recode(
                        as.factor(frace),"1" = "White", "2" = "Black", "3" = "Asian", "4" = "Puerto Rican", "8" = "Other", "9" = "Unknown"),
         malform = recode(
                        as.factor(malform),"0" = "Absent", "1" = "Present"),
         mrace = recode(
                        as.factor(mrace),"1" = "White", "2" = "Black", "3" = "Asian", "4" = "Puerto Rican", "8" = "Other")
         )

map(birthwt, ~sum(is.na(.)))
```

There are no missing values, and the 4 categorical variables are now factors.

### Proposed Regression Model

I'm using the step function, followed by checking the LM Adjusted R-Squared, and RSS to determine the optimal model. I'm hiding the results of this code chunk, as they take up a lot of space (especially the step function), but I will summarize them below.

```{r p1 regression model, results = F}
prop_reg_model1 <- step(lm(bwt ~., data = birthwt),direction = "backward")

summary(prop_reg_model1)

prop_reg_model2 <- lm(formula = bwt ~ babysex + bhead + blength + delwt + 
    gaweeks + mheight + mrace + parity + ppwt + smoken, data = birthwt)

summary(prop_reg_model2)

anova(prop_reg_model2,prop_reg_model1)

prop_reg_model3 <- lm(formula = bwt ~ babysex + bhead + blength + delwt + 
    gaweeks + mheight + mrace + ppwt + smoken, data = birthwt)

summary(prop_reg_model3)

anova(prop_reg_model3,prop_reg_model2)
```

I first built the model using the step function with direction = "backwards", which initially builds the model with all variables as predictors, then removes them one at a time and tests if the AIC decreases (which is indicative of better model fit). The model that the step function returned was:

lm(formula = bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken, data = birthwt)

I checked a summary of the model, and then removed the least significant variables and checked to see if the model's Adjusted R-Squared decreased significantly, and used an anova to test if the RSS was significantly decreased due to the additional variable. What I found was that removing "fincome" did not decrease the adjusted R-squared very much, and including "fincome" did not decrease the RSS very significantly, so I removed fincome from the model as well. I checked if removing "parity" would be similar, but the adjusted R-squared did decrease a bit, and an anova test suggested that including "parity" actually did decrease the RSS to a significant degree, so I left "parity" in the model, and my final model was:

lm(formula = bwt ~ babysex + bhead + blength + delwt + gaweeks + mheight + mrace + parity + ppwt + smoken, data = birthwt)
    
### Plotting Residuals Against Fitted Values

```{r p1 plot}
birthwtdf <- add_residuals(birthwt, prop_reg_model2)
birthwtdf <- add_predictions(birthwtdf, prop_reg_model2)

birthwtdf %>%
  ggplot(aes(x=pred,y=resid)) + 
  geom_point(alpha=.5)
```

The spread of the residuals looks random, which is a good indication that our model did not miss an important predictor.

### Comparing the model with 2 others by plotting prediction error distributions

```{r p1 model comparison}
model1 <- lm(bwt ~ blength + gaweeks, data = birthwt)
model2 <- lm(bwt ~ bhead * blength * babysex, data = birthwt)

cv_df <- crossv_mc(birthwt,100)

cv_df2 <- cv_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

cv_df3 <- cv_df2 %>% 
  mutate(my_proposed_mod  = map(train, ~lm(formula = bwt ~ babysex + bhead + blength + delwt + gaweeks + mheight + mrace + parity + ppwt + smoken, data = birthwt)),
         model1  = map(train, ~lm(bwt ~ blength + gaweeks, data = birthwt)),
         model2  = map(train, ~lm(bwt ~ bhead * blength * babysex, data = birthwt))) %>% 
  mutate(rmse_my_mod = map2_dbl(my_proposed_mod, test, ~rmse(model = .x, data = .y)),
         rmse_mod1 = map2_dbl(model1, test, ~rmse(model = .x, data = .y)),
         rmse_mod2 = map2_dbl(model2, test, ~rmse(model = .x, data = .y)))

cv_df3 %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

The RMSE is the lowest for the model I created, which suggests it is the best fit model of the three. Mod2 is fairly close, and mod1 is not as good a fit.

## Problem 2

### Loading the data, Bootstrap, models, and results

```{r p2}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())

boots_df <- weather_df %>%
  bootstrap(n=5000) %>%
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance),
    results2 = map(models, broom::tidy)) 
```

### Plotting r.squared and constructing a 95% confidence interval

```{r p2 rsquared}
boots_df_r2 <- boots_df %>%
  select(-strap, -models) %>% 
  unnest(results) %>%
  select(.id,r.squared)

boots_df_r2 %>% 
  pull(r.squared) %>%
  as.vector() %>%
  quantile(probs=c(0.025, 0.975))
```


### Plotting log(b0*b1) and constructing a 95$ confidence interval

```{r p2 logb0b1}
boots_df_logb0b1 <- boots_df %>%
  select(-strap, -models) %>% 
  unnest(results2) %>%
  select(.id,term,estimate) %>%
  pivot_wider(names_from = term,
              values_from = estimate) %>%
  janitor::clean_names() %>%
  mutate(logb0b1 = log(intercept*tmin))

boots_df_logb0b1 %>% 
  pull(logb0b1) %>%
  as.vector() %>%
  quantile(probs=c(0.025, 0.975))
```

